% spell-checker: disable %
%% Use AASTeX class, version 6.1
%% Allow for additional class options such as,
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		            wider left and right margins. This uses the Daniel
%% 		            Foreman-Mackey and David Hogg design.
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers

\documentclass[modern]{aastex63}
%% Include packages
\usepackage{amsmath}
\usepackage{calc}
\include{pythontex}
%% Custom commands
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\AR}{active region}
\newcommand{\dem}{$\mathrm{EM}(T)$}
\newcommand{\twait}[1][]{t_{\textup{wait}#1}}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Section}
\renewcommand{\subsubsectionautorefname}{Section}
%% Paper Aliases
\defcitealias{barnes_understanding_2019}{Paper I}
\defcitealias{viall_survey_2017}{VK17}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Body                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Title and Authors                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Understanding Heating in Active Region Cores through Machine Learning II. Classifying Observations}
\author[0000-0001-9642-6089]{W. T. Barnes}
\affiliation{National Research Council Postdoctoral Research Associate residing at the Naval Research Laboratory, Washington, D.C. 20375}
\affiliation{Department of Physics \& Astronomy, Rice University, Houston, TX 77005-1827}
\author[0000-0002-3300-6041]{S. J. Bradshaw}
\affiliation{Department of Physics \& Astronomy, Rice University, Houston, TX 77005-1827}
\author[0000-0003-1692-1704]{N. M. Viall}
\affiliation{NASA Goddard Space Flight Center, Greenbelt, MD 20771}
\correspondingauthor{W. T. Barnes}
\email{will.barnes.ctr@nrl.navy.mil}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Abstract                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Constraining the frequency of energy deposition in magnetically-closed \AR{} cores requires sophisticated hydrodynamic simulations of the coronal plasma and detailed forward modeling of the optically-thin line-of-sight integrated emission.
However, understanding which set of model inputs best matches a set of observations is complicated by the need for any proposed heating model to simultaneously satisfy multiple observable constraints.
In this paper, we train a random forest classification model on a set of forward-modeled observable quantities, namely the emission measure slope, the peak temperature of the emission measure distribution, and the time lag and maximum cross-correlation between multiple pairs of AIA channels.
We then use our trained model to classify the heating frequency in every pixel of \AR{} NOAA 1158 using the observed emission measure slopes, peak temperatures, time lags, and maximum cross-correlations and are able to map the heating frequency across the entire active region.
We find that high-frequency heating dominates in the inner core of the \AR{} while intermediate frequency dominates closer to the periphery of the \AR{}.
Additionally, we assess the importance of each observed quantity in our trained classification model and find that the emission measure slope is the dominant feature in deciding with which heating frequency a given pixel is most consistent.
The technique presented here offers a very promising and widely applicable method for assessing observations in terms of detailed forward models given an arbitrary number of observable constraints.
\end{abstract}
%% Keywords
\keywords{Active solar corona (1988), Astronomy data analysis (1858), Solar extreme ultraviolet emission (1493), Random Forests (1935)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Sections                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sections/intro}
\input{sections/methods}
\input{sections/results}
\input{sections/discussion}
\input{sections/summary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Acknowledgment                            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
This research makes use of \added{version 0.9.5 \citep{stuart_mumford_2018_2155946}} of sunpy, an open-source and free community-developed solar data analysis package written in Python \citep{the_sunpy_community_sunpy_2020}.
\added{We use v0.9.5 in this work to maintain consistency with the software environment used in \citetalias{barnes_understanding_2019} which was completed prior to the v1.0 release of sunpy.}
SJB and WTB were supported by the NSF through CAREER award AGS-1450230.
WTB was supported by NASA’s \textit{Hinode} program.
\textit{Hinode} is a Japanese mission developed and launched by ISAS/JAXA with NAOJ as a domestic partner and NASA and STFC (UK) as international partners.
It is operated by these agencies in cooperation with ESA and NSC (Norway).
The work of NMV was supported by the NASA Supporting Research program.
The complete source of this paper, including the data, code, and instructions for training the classification model, can be found at \href{https://github.com/rice-solar-physics/synthetic-observables-paper-observations}{github.com/rice-solar-physics/synthetic-observables-paper-observations}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Facilities                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\facility{SDO(AIA)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Software                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\software{
    astropy \citep[v3.1.0,][]{the_astropy_collaboration_astropy_2018,the_astropy_collaboration_2018_4080996},
	dask \citep[v1.0.0,][]{rocklin_dask:_2015},
	drms \citep[v0.5,][]{glogowski_drms_2019,kolja_glogowski_2019_2572850},
    matplotlib \citep[v3.0.2,][]{hunter_matplotlib_2007,thomas_a_caswell_2018_1482099},
	numpy \citep[v1.15.4,][]{harris_array_2020},
	PythonTeX \citep[v0.16,][]{poore_pythontex_2015},
    scikit-learn \citep[v0.20,][]{pedregosa_scikit-learn_2011,olivier_grisel_2019_2582066},
	seaborn \citep[v0.9.0,][]{michael_waskom_2018_1313201},
	scipy \citep[v1.1.0,][]{virtanen_scipy_2020, pauli_virtanen_2018_1241501},
	SolarSoftware \citep{freeland_data_1998},
    sunpy \citep[v0.9.5,][]{stuart_mumford_2018_2155946}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   References                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{aasjournal.bst}
\bibliography{references.bib,software.bib}

\listofchanges

\end{document}
    